Making Deep Q-learning Methods Robust to Time Discretization

### 2019-01-19 paper/icml_drau/framework.tex

As a consequence, in exact continuous time,
$Q^\pi$ is equal to $V^\pi$:  it does not bear \emph{any} information on the ranking of actions, and
thus cannot be used to select actions that yields higher returns.
There is no time continuous $Q$-learning.

>>>>

As a consequence, in exact continuous time,
$Q^\pi$ is equal to $V^\pi$:  it does not bear \emph{any} information on the ranking of actions, and
thus cannot be used to select actions with higher returns.
There is no continuous-time $Q$-learning.
